---
title: "RWorksheet_Talon#4c"
author: "Cedric Mikhail Talon"
date: "2023-11-22"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#1
#a. Show your solutions on how to import a csv file into the environment.
```{r}

library(readr)

mpg <- read.csv("mpg.csv")
mpg


```
#b.  Which variables from mpg dataset are categorical?
```{r}
str(mpg)
```
#c.  Which are continuous variables?
```{r}
 conti_var <- c("displ","year","cyl","cty","hwy")
 conti_var
```
#2. Which manufacturer has the most models in this data set?
```{r}
manufacturer <-
```
#a. Group the manufacturers and find the unique models. Show your codes and result
```{r}

```
#b. Graph the result by using plot() and ggplot(). Write the codes and its result.
```{r}

```
#2. Same dataset will be used. You are going to show the relationship of the modeland the manufacturer.
```{r}

```
#a. What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show?
```{r}

```
#b. For you, is it useful? If not, how could you modify the data to make it more informative?
```{r}

```
#3. Plot the model and the year using ggplot(). Use only the top 20 observations. Write the codes and its results.
```{r}

```
#4. Using the pipe (%>%), group the model and get the number of cars per model. Show codes and its result
```{r}

```
#a. Plot using geom_bar() using the top 20 observations only. The graphs shoudl have a title, labels and colors. Show code and results.
```{r}

```
#b. Plot using the geom_bar() + coord_flip() just like what is shown below. Show codes and its result.

```{r}

```
#5. Plot the relationship between cyl - number of cylinders and displ - engine displacement using geom_point with aesthetic color = engine displacement. Title should be “Relationship between No. of Cylinders and Engine Displacement”.
```{r}

```
#a. How would you describe its relationship? Show the codes and its result.
```{r}

```
#6. Plot the relationship between displ (engine displacement) and hwy(highway miles per gallon). Mapped it with a continuous variable you have identified in #1-c. What is its result? Why it produced such output?
```{r}

```
#
```{r}

```
#
```{r}

```