---
title: "RWorksheet_Talon#4c"
author: "Cedric Mikhail Talon"
date: "2023-11-22"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#1
#a. Show your solutions on how to import a csv file into the environment.
```{r}

library(readr)

mpg <- read.csv("mpg.csv")
mpg


```
#b.  Which variables from mpg dataset are categorical?

1. Transmission        
2. Model                  
3. class      
4. Drive Train                 
5. Fuel type
6. manufacturer
```{r}

library(dplyr)
data(mpg)
categ_col <- mpg %>% select_if(is.factor) %>% colnames()



print(categ_col)

```

#c.  Which are continuous variables?

1. x 
2. displ 
3. year
4. cyl
5. cty
6. hwy

#2. Which manufacturer has the most models in this data set?
Most model: dodge
Most variations: caravan 2wd

```{r}
manu <- table(mpg$manufacturer)

maxmod_Manu <- as.character(names(manu))[which.max(manu)]

cat("The most model is: ",maxmod_Manu,"\n ")

tablyat <- table(mpg$model)
maxVarmodel <- as.character(names(tablyat))[which.max(tablyat)]

cat("Le most variations is: ",maxVarmodel)
```
#a. Group the manufacturers and find the unique models. Show your codes and result
```{r}

library(dplyr)

model <- data.frame(Manufacturer = mpg$manufacturer,
                     Model = mpg$model)
model

pinasahi <- unique(model)
pinasahi

```
#b. Graph the result by using plot() and ggplot(). Write the codes and its result.
```{r}

library(ggplot2)

UniqueModels <- as.factor(pinasahi$Manufacturer)
baho <- plot(as.factor(UniqueModels),
                             main = "Le Unique Model of Manufacturer",
                             xlab = "Le Manufacturer", 
                             ylab = "Le Number of ze Unique Models",
                             cex.names = 0.5,
                             las = 2)
baho

```
#2. Same dataset will be used. You are going to show the relationship of the modeland the manufacturer.
#a. What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show?
```{r}

library(ggplot2)

ggplot(mpg,aes(model,manufacturer)) + 
   geom_point() + 
  theme(plot.title = element_text(hjust = 0.9),
        axis.text.x = element_text(angle = 44, hjust = 1))

```

#b. For you, is it useful? If not, how could you modify the data to make it more informative?
Yes, yes it is useful because you have been given an idea of many models are being produced by different manufacturers

#3. Plot the model and the year using ggplot(). Use only the top 20 observations. Write the codes and its results.
```{r}

mainpopgirls <- head(mpg,20)
mainpopgirls

```
#4. Using the pipe (%>%), group the model and get the number of cars per model. Show codes and its result
```{r}

library(dplyr)



datagrupo <- mpg %>% group_by(model) %>% summarise(count = n()) 
datagrupo

```
#a. Plot using geom_bar() using the top 20 observations only. The graphs shoudl have a title, labels and colors. Show code and results.
```{r}

observation_haki <- head(datagrupo,20)
observation_haki

plot <- ggplot(observation_haki,
       aes(x = model,
           y = count,
           fill = model)) + 
  geom_bar(stat = "identity") +
   labs(title = "Top 20 Most Popular Models of a car", 
       x = "Models",
       y = "The Number of Cars") +
   theme_minimal() +
  theme(plot.title = element_text(hjust = 0.8),
        axis.text.x = element_text(angle = 44, hjust = 1))

observation_haki

```
#b. Plot using the geom_bar() + coord_flip() just like what is shown below. Show codes and its result.

```{r}

observation_haki <- ggplot(observation_haki,
       aes(x = reorder(model, count),
           y = count,
           fill = model)) + 
  geom_bar(stat = "identity") +
  coord_flip()+
  
  labs(title = "Le Number of Cars Models", 
       x = "Models",
       y = "Le Number of Cars") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 44, hjust = 1))

observation_haki

```
#5. Plot the relationship between cyl - number of cylinders and displ - engine displacement using geom_point with aesthetic color = engine displacement. Title should be “Relationship between No. of Cylinders and Engine Displacement”.
```{r}

relationship <- data.frame(Cylinder = mpg$cyl,Engine_Displacement = mpg$displ)

relationship

relationship <- ggplot(relationship,
                            aes(x = Cylinder, y = Engine_Displacement, color = Engine_Displacement))+
                              geom_point()+
                              labs(title = "number of cylinders/ engine displacement relationship",
                                   
                                   
                                   x = "Numero la Cylinders",
                                   y = "Engine Displacement")+
  
scale_color_gradient(low = "orange", high = "red")+
theme(plot.title = element_text(hjust = 0.4))


relationship

```
#a. How would you describe its relationship? Show the codes and its result.

Cylinder increases, Displacement also increases.


#6. Plot the relationship between displ (engine displacement) and hwy(highway miles per gallon). Mapped it with a continuous variable you have identified in #1-c. What is its result? Why it produced such output?
```{r}

hwy_relationship <- ggplot(mpg, aes(x = displ, y = hwy, color = cty)) +
  geom_point() +
  labs(title = "Engine Displacement and Highway MPG Relationship",
       x = "Le Engine Displacement",
       y = "Le Highway MPG")

hwy_relationship

```
#6. Import the traffic.csv onto your R environment.
```{r}

library(readr)
traffic <- read.csv("traffic.csv")

numofObservation <- nrow(traffic)
numofObservation

numofVarations <- ncol(traffic)
numofVarations

varations <- colnames(traffic)
varations
```
#6b. subset the traffic dataset into junctions. What is the R codes and its output?

```{r}
junctions1 <- subset(traffic, Junction == 1)

junctions2 <- subset(traffic, Junction == 2)

junctions3 <- subset(traffic, Junction == 3)

junctions4 <- subset(traffic, Junction == 4)

```

#6c. Plot each junction in a using geom_line(). Show your solution and output.
```{r}
junction1plot <- ggplot(junctions1, aes(x = as.Date(junctions1$DateTime), y = Vehicles)) + geom_line() + scale_x_date(date_labels = "%b-%Y") + theme(legend.position = "none") + labs(title = "Junction 1", x = "Time", y = "Number of Vehicles")

junction1plot

junction2plot <- ggplot(junctions2, aes(x = as.Date(junctions2$DateTime), y = Vehicles)) + geom_line() + scale_x_date(date_labels = "%b-%Y") + theme(legend.position = "none") + labs(title = "Junction 2", x = "Time", y = "Number of Vehicles")

junction2plot

junction3plot <- ggplot(junctions3, aes(x = as.Date(junctions3$DateTime), y = Vehicles)) + geom_line() + scale_x_date(date_labels = "%b-%Y") + theme(legend.position = "none") + labs(title = "Junction 3", x = "Time", y = "Number of Vehicles")

junction3plot

junction4plot <- ggplot(junctions4, aes(x = as.Date(junctions4$DateTime), y = Vehicles)) + geom_line() + scale_x_date(date_labels = "%b-%Y") + theme(legend.position = "none") + labs(title = "Junction 4", x = "Time", y = "Number of Vehicles")

junction4plot


```
#7. From alexa_file.xlsx, import it to your environment

#7a. How many observations does alexa_file has? What about the number of columns? Show your solution and answer.
ans. There are 3150 observations and 5 number of columns.
```{r}
library(readxl)

alexaData <-  read_excel("/cloud/project/RWorkSheet#4/4C/alexa_file2.xlsx")

numofObservation<- nrow(alexaData)
numofObservation

numColoumns <- ncol(alexaData)
numColoumns



```

#7b. group the variations and get the total of each variations. Use dplyr package. Show solution and answer

```{r}
varCounts <- alexaData %>%
  count(variation)

varCounts
```
#7c. Plot the variations using the ggplot() function. What did you observe? Complete the details of the graph. Show solution and answer.


```{r}
alexaPlot <- ggplot(alexaData, aes(x = variation)) + geom_bar(fill = "orange") + labs(title = "Variations", x = "Variation", y = "Count") + theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 44, hjust = 1))


alexaPlot

# The graph depicts the distribution of variations and their respective counts. Each bar represents a specific variant, and the height of the bar shows the count of that variation.
```

#7d. Plot a geom_line() with the date and the number of verified reviews. Complete the details of the graphs. Show your answer and solution
```{r}
library(dplyr)

alexaData$date <- as.Date(alexaData$date)

alexaData$month <- format(alexaData$date, "%m")

countMonth <- alexaData %>% count(month)
countMonth

monthly_revCount <- table(countMonth)
monthly_revCount

alexa <- ggplot(countMonth, aes(x = month, y = n, group = 1)) +
  geom_line(color = "pink") +
  labs(title = "Number of Reviews Over Time that is Verified",
       x = "Date",
       y = "Number of Reviews Verified")

alexa

```


#7e. Get the relationship of variations and ratings. Which variations got the most highest in rating? Plot a graph to show its relationship. Show your solution and answer.

```{r}

variationR <- alexaData %>%
  group_by(variation) %>%
  summarise(avg_rating = mean(rating))

variationR

highest_ratings <- variationR %>%
  filter(avg_rating == max(avg_rating))

highest_ratings 

# The highest rating is the walnut

ggplot(variationR, aes(x = variation, y = avg_rating)) +
  geom_bar(stat = "identity", fill = "blue") +
  labs(title = "Average Ratings by Variation",
       x = "Variation",
       y = "Average Rating") + theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 44, hjust = 1))



```